---
title: "FinVol"
author: "Ardit Zhuniqi & Arbian Halilaj"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

## R Markdown

```{r, include=FALSE}
library(readxl)
library(xtable)
library(fBasics)
library(stargazer)
library(rugarch)
library(rmgarch)
library(car)
library(ggplot2)
library(xts)
library(parallel)
library(forecast)
library(tseries)
library(quantmod)
library(urca)
library(psych)
library(knitr)
library(PerformanceAnalytics)
library(dplyr)
library(fGarch)
library(DataCombine)
library(limma) # Student's t
```

# Data preparation
```{r}
#data_clean <- read_excel("C:/Users/ardit/OneDrive - Universität St.Gallen/Universität St. Gallen/Master/Financial Volatility/Group_Assignment/final_data.xlsx")

data_clean <- read_excel("/Users/arbiun/OneDrive - Universität St.Gallen/Group_Assignment/final_data.xlsx")

data_clean$log_Crypto <- Delt(data_clean$`Last Price Crypto`, type = "log")
data_clean$log_STOXX <- Delt(data_clean$`Last Price STOXX`, type = "log")
data_clean$log_BONDS <- Delt(data_clean$`Last Price BONDS`, type = "log")
data_clean$log_Commodities <- Delt(data_clean$`Last Price COMMODITIES`, type = "log")

data <- data_clean[-1,]
```

# Charts
```{r, fig.height=5}
data_ts <- xts(data[, -1], order.by=as.Date(data$Date));
events_covid <- xts(letters[1:2], 
              as.Date(c("2020-01-30", "2020-03-11")))

par(mfrow=c(1,1))
plot.xts(data_ts$`Last Price Crypto`, main = 'Bitwise 100 Index Prices')
addEventLines(events_covid, srt=90, pos=2, col = "red")
plot.xts(data_ts$log_Crypto, main = 'Bitwise 100 Index Log Returns')
addEventLines(events_covid, srt=90, pos=2, col = "red")
```

```{r, fig.height=5}
plot.xts(data_ts$`Last Price STOXX`, main = 'MSCI World Index Prices')
addEventLines(events_covid, srt=90, pos=2, col = "red")
plot.xts(data_ts$log_STOXX, main = 'MSCI World Index Log Returns')
addEventLines(events_covid, srt=90, pos=2, col = "red")
```

```{r, fig.height=5}
plot.xts(data_ts$`Last Price BONDS`, main = 'Bloomberg Barclays Global Agg Bond Index Prices')
addEventLines(events_covid, srt=90, pos=2, col = "red")
plot.xts(data_ts$log_BONDS, main = 'Bloomberg Barclays Global Agg Bond Index Log Returns')
addEventLines(events_covid, srt=90, pos=2, col = "red")
```

```{r, fig.height=5}
plot.xts(data_ts$`Last Price COMMODITIES`, main = 'Bloomberg Commodity Index Prices')
addEventLines(events_covid, srt=90, pos=2, col = "red")
plot.xts(data_ts$log_Commodities, main = 'Bloomberg Commodity Index Log Returns')
addEventLines(events_covid, srt=90, pos=2, col = "red")
```

# Descriptive Statistics
```{r}

# Raw series of cryptos:  
knitr::kable(psych::describe(data_clean$`Last Price Crypto`), "simple")

# Log returns of cryptos: 
knitr::kable(psych::describe(data$log_Crypto), "simple")

# Raw series of stocks: 
knitr::kable(psych::describe(data$`Last Price STOXX`), "simple")

# Log returns of stocks: 
knitr::kable(psych::describe(data$log_STOXX), "simple")

# Raw series of bonds: 
knitr::kable(psych::describe(data$`Last Price BONDS`), "simple")

# Log returns of bonds: 
knitr::kable(psych::describe(data$log_BONDS), "simple")

# Raw series of commodities:
knitr::kable(psych::describe(data$`Last Price COMMODITIES`), "simple")

# Log returns of commodities:
knitr::kable(psych::describe(data$log_Commodities), "simple")


```

# Analysis of the crypto series
##Unit Root Test: Testing stationarity on cryptos
```{r}
# Raw series
augmented_df_test <- ur.df(data$`Last Price Crypto`, selectlags = "BIC")
summary(augmented_df_test)

# Differenced series
augmented_df_test <- ur.df(DropNA(data$log_Crypto), selectlags = "BIC")
summary(augmented_df_test)

# The Null-Hypothesis is that we have an unit root.
# The test clearly rejects the null on every common significance level, 
# resulting that we can assume stationarity on both, the raw series (????)
# and the differenced series.
```
## Box-Ljung Test
```{r}
Box.test(data$`Last Price Crypto`, lag = 20, type = "Ljung")
Box.test(data$log_Crypto, lag = 20, type = "Ljung")
```
## ACF and PAFC
```{r}
par(mfrow=c(2,2))

#ACF and PACF on raw crypto series.
Acf(data$`Last Price Crypto`, type= "correlation", lag.max = 15,
    main= "ACF Cryptos")
Pacf(data$`Last Price Crypto`, lag= 15, main= "PACF of differenced process")

#ACF and PACF differenced process
Acf(data$log_Crypto, type= "correlation", lag= 15, main= "ACF of differenced process Cryptos")
Pacf(data$log_Crypto, lag= 15, main= "PACF of differenced process")
```

## ARIMA Modelling
```{r}

#Identify the ARIMA model
#Time series 1:
aic1 = matrix(NA,8,8)
bic1 = matrix(NA,8,8)
for(p in 0:7)
{
  for(q in 0:7)
  {
    a.p.q = Arima(data$log_Crypto,order=c(p,0,q),include.mean=TRUE)
    aic.p.q = a.p.q$aic
    bic.p.q = BIC(a.p.q)
    aic1[p+1,q+1] = aic.p.q
    bic1[p+1,q+1] = bic.p.q
  }
}
aic1 
bic1 # 0,0 has the lowest BIC

arima_model_BIC <- Arima(data$log_Crypto, order = c(0,0,0), include.mean=TRUE)
summary(arima_model_BIC)
```

## Testing for ARCH/GARCH effects using the LM test
```{r}
# The LM test is equivalent to a portmanteau test on the squares.
# Finally, with the LM test we have a formal test to to statistically check the existence of an ARCH / GARCH effect.
LM=function(x,h)
{
  n=length(x)
  x2=x^2-mean(x^2)
  dat<-matrix(,n-h,h+1)
  for (i in 1:(h+1))
  {
    dat[,i]=x2[(h+2-i):(n-i+1)]
  }
  a=lm(dat[,1]~dat[,2:(h+1)])
  r2=summary(a)$r.squared
  print(r2 * n)
  print(1-pchisq(r2*n,h))
}

LM(data$log_Crypto, 25) # The results show that we have clearly ARCH / GARCH effects in our series.

# AFC and PAFC of the residuals and the squared residuals of the ARIMA (0,0) model
par(mfrow=c(2,2))
par(oma=c(0,0,5,0))
# windows(width=9, height=6)
Acf(arima_model_BIC$residuals, type= "correlation", lag= 15, main= "ACF of residuals Cryptos")
Pacf(arima_model_BIC$residuals, lag= 15, main= "PACF of residuals")

Acf(arima_model_BIC$residuals^2, type= "correlation", lag= 15, main= "ACF of squared residuals Cryptos")
Pacf(arima_model_BIC$residuals^2, lag= 15, main= "PACF of squared residuals")
title("TITLE" , outer=TRUE)

```

## ARMA - GARCH joint order selection
## Modeling the GARCH
```{r}
#Select model with smallest BIC (if prediction is the objective)
final.bic = Inf
final.order.arma = c(0,0)
final.order.garch = c(0,0)
for (p in 0:3) for (q in 0:3) for (d in 0:2) for (w in 0:2)
{
  spec = ugarchspec(variance.model=list(garchOrder=c(p,q)),
                    mean.model=list(armaOrder=c(d, w), include.mean=T),
                    distribution.model="std")    
  fit = ugarchfit(spec, data$log_Crypto, solver = 'hybrid')
  current.bic = infocriteria(fit)[2] 
  if (current.bic < final.bic) 
  {
    final.bic = current.bic
    final.order.arma = c(d, w)
    final.order.garch = c(p,q)
  }
}
final.order.arma
final.order.garch

#arma 1 1 garch 2 1
```

## Fit the ARMA - GARCH model
```{r}
m1=garchFit(data$log_Crypto~ arma(1,1) + garch(2,1),trace=F,data= data$log_Crypto, cond.dist = c("std"), include.mean = TRUE)
summary(m1)
m1=garchFit(data$log_Crypto~ arma(1,1) + garch(1,1),trace=F,data= data$log_Crypto, cond.dist = c("std"), include.mean = TRUE)
summary(m1)

# Although the optimization showed that GARCH (2, 1) reflects the lowest BIC, GARCH (1,1) was chosen due to over fitting and the alpha 2 is not significant. 
# Additionally, GARCH (1, 1) has only a marginally higher BIC.

par(mfrow=c(2,2))
standardized_residuals <- residuals(m1, standardize = T) # standardize the residuals from the previous GARCH model
# AFC and PAFC on GARCH residuals
acf_residuals_BIC <- Acf(standardized_residuals, lag = 20, type = "correlation",main = "ACF ARMA (1,1) - GARCH (1,1) residuals")
pacf_residuals_BIC <- Pacf(standardized_residuals, lag = 20,main = "PACF ARMA (1,1) - GARCH (1,1) residuals") 

# AFC and PAFC on GARCH squared residuals
acf_squared_residuals_BIC <- Acf(standardized_residuals^2, lag = 20, type = "correlation",main = "ACF ARMA (1,1) - GARCH (1,1) squared residuals")
pacf_squared_residuals_BIC <- Pacf(standardized_residuals^2, lag = 20, main = "PACF ARMA (1,1) - GARCH (1,1) squared residuals")

Box.test(standardized_residuals, lag = 20, type = "Ljung")
Box.test(standardized_residuals^2, lag = 5, type = "Ljung")
```

## Check residuals for normality
```{r}
#fat tails
jarque.bera.test(standardized_residuals)
par(mfrow=c(1,2))
qqnorm(standardized_residuals)
qqline(standardized_residuals)
qqt(standardized_residuals, df = 4)
qqline(standardized_residuals)
# The Jarque Bera Test clearly rejects the fact that the standardized residuals of the GARCH model are normally distributed.
# This can be also seen in the QQ-Plot, concluding that we have fat tails.
```


# Preparation for DCC-GARCH model
In order to estimate the parameters of the DCC-GARCH model, we need the results and the model specifications from the previous analysis. Hence, we need the results from the analysis of stocks, bonds and commodities to estimate the parameters of the DCC-GARCH model.

## Stocks
```{r}
########################################## 1.) Testing stationarity ####################################################
# 1.1) Unit Root Test

# On raw series
augmented_df_test <- ur.df(data$`Last Price STOXX`, selectlags = "BIC")
summary(augmented_df_test)

# On differenced series
augmented_df_test <- ur.df(data$log_STOXX, selectlags = "BIC")
summary(augmented_df_test)

# The test clearly shows that there is stationarity on the differenced series on stocks.
# However, it can be obtainted, that we also have stationarity on our raw series on the 95% CI.

# 1.2) Box-Ljung Test
Box.test(data$`Last Price STOXX`, lag = 20, type = "Ljung")
Box.test(data$log_STOXX, lag = 20, type = "Ljung")

# 1.3) AFC and PAFC
par(mfrow=c(2,2))

#ACF and PACF on raw stock series.
Acf(data$`Last Price STOXX`, type= "correlation", lag.max = 15,
    main= "ACF raw stock series")
Pacf(data$`Last Price STOXX`, lag= 15, main= "PACF raw stock series")

#ACF and PACF differenced process
Acf(data$log_STOXX, type= "correlation", lag= 15, main= "ACF of differenced process")
Pacf(data$log_STOXX, lag= 15, main= "PACF of differenced process")

########################################################################################################################

########################################## 2.) ARMA modeling ###########################################################
# 2.1) Identify the ARIMA model
aic1 = matrix(NA,8,8)
bic1 = matrix(NA,8,8)
for(p in 0:7)
{
  for(q in 0:7)
  {
    a.p.q = Arima(data$log_STOXX,order=c(p,0,q),include.mean=TRUE)
    aic.p.q = a.p.q$aic
    bic.p.q = BIC(a.p.q)
    aic1[p+1,q+1] = aic.p.q
    bic1[p+1,q+1] = bic.p.q
  }
}
aic1 
bic1 # 3,2 has the lowest BIC

# 2.2) Using the results for the optimal ARIMA model
arima_model_BIC <- Arima(data$log_STOXX, order = c(3,0,2), include.mean=TRUE)
summary(arima_model_BIC)

########################################################################################################################

########################################## 3.) Testing for ARCH effects ################################################
# 3.1) Using the LM test
LM=function(x,h)
{
  n=length(x)
  x2=x^2-mean(x^2)
  dat<-matrix(,n-h,h+1)
  for (i in 1:(h+1))
  {
    dat[,i]=x2[(h+2-i):(n-i+1)]
  }
  a=lm(dat[,1]~dat[,2:(h+1)])
  r2=summary(a)$r.squared
  print(r2 * n)
  print(1-pchisq(r2*n,h))
}

LM(data$log_STOXX, 20) # The results show that we have clearly ARCH / GARCH effects in our series.

# 3.2) AFC and PAFC of the residuals and the squared residuals of the ARIMA (3,2) model
par(mfrow=c(2,2))
Acf(arima_model_BIC$residuals, type= "correlation", lag= 15, main= "ACF of residuals (Stocks)")
Pacf(arima_model_BIC$residuals, lag= 15, main= "PACF of residuals (Stocks)")

Acf(arima_model_BIC$residuals^2, type= "correlation", lag= 15, main= "ACF of squared residuals (Stocks)")
Pacf(arima_model_BIC$residuals^2, lag= 15, main= "PACF of squared residuals (Stocks)")

########################################################################################################################

########################################## 4.) ARMA-GARCH modeling #####################################################
# 4.1 ARMA - GARCH joint order selection
final.bic = Inf
final.order.arma = c(0,0)
final.order.garch = c(0,0)
for (p in 0:3) for (q in 0:3) for (d in 0:2) for (w in 0:2)
{
  spec = ugarchspec(variance.model=list(garchOrder=c(p,q)),
                    mean.model=list(armaOrder=c(d, w), include.mean=T),
                    distribution.model="std")    
  fit = ugarchfit(spec, data$log_STOXX, solver = 'hybrid')
  current.bic = infocriteria(fit)[2] 
  if (current.bic < final.bic) 
  {
    final.bic = current.bic
    final.order.arma = c(d, w)
    final.order.garch = c(p,q)
  }
}
final.order.arma
final.order.garch
# Select model with smallest BIC (if prediction is the objective). This would be ARMA (0, 0) and GARCH (1, 1)

# 4.2 Fit the GARCH model
m1_stocks=garchFit(data$log_STOXX~ arma(0,0) + garch(1,1),trace=F,data= data$log_STOXX, cond.dist = c("std"), include.mean = TRUE)
summary(m1_stocks)

# 4.3 AFC and PAFC on GARCH residuals and squared residuals
par(mfrow=c(2,2))
standardized_residuals <- residuals(m1_stocks, standardize = T) # standardize the residuals from the previous GARCH model
# AFC and PAFC on GARCH residuals
acf_residuals_BIC <- Acf(standardized_residuals, lag = 20, type = "correlation",main = "ACF ARMA (0,0) - GARCH (1,1) residuals")
pacf_residuals_BIC <- Pacf(standardized_residuals, lag = 20,main = "PACF ARMA (0,0) - GARCH (1,1) residuals") 
# However, our residuals reveal several boundary violations.

# AFC and PAFC on GARCH squared residuals
acf_squared_residuals_BIC <- Acf(standardized_residuals^2, lag = 20, type = "correlation",main = "ACF ARMA (0,0) - GARCH (1,1) squared residuals")
pacf_squared_residuals_BIC <- Pacf(standardized_residuals^2, lag = 20, main = "PACF ARMA (0,0) - GARCH (1,1) squared residuals")
# However, our squared residuals reveal several boundary violations.

# 4.4 Check residuals for normality
#fat tails
jarque.bera.test(standardized_residuals)
qqnorm(standardized_residuals) # Frage: Asymmetry??
qqline(standardized_residuals)

# The Jarque Bera Test clearly rejects the fact that the standardized residuals of the GARCH model are normally distributed.
# This can be also seen in the QQ-Plot, concluding that we have fat tails.
```

## BONDS
```{r}
################################### 1.) Testing stationarity ########################################
# 1.1) Unit Root Test

# On raw series
augmented_df_test <- ur.df(data$`Last Price BONDS`, selectlags = "BIC")
summary(augmented_df_test)

# On differenced series
augmented_df_test <- ur.df(data$log_BONDS, selectlags = "BIC")
summary(augmented_df_test)

# The test clearly shows that there is stationarity on the differenced series.

# 1.2) Box-Ljung Test
Box.test(data$`Last Price BONDS`, lag = 20, type = "Ljung")
Box.test(data$log_BONDS, lag = 20, type = "Ljung")

# 1.3) AFC and PAFC
par(mfrow=c(2,2))

#ACF and PACF on raw bond series.
Acf(data$`Last Price BONDS`, type= "correlation", lag.max = 15,
    main= "ACF raw bond series")
Pacf(data$`Last Price BONDS`, lag= 15, main= "PACF raw bond series")

#ACF and PACF differenced process
Acf(data$log_BONDS, type= "correlation", lag= 15, main= "ACF of differenced process")
Pacf(data$log_BONDS, lag= 15, main= "PACF of differenced process")

#################################### 2.) ARMA modeling ##############################################
# 2.1) Identify the ARIMA model
aic1 = matrix(NA,8,8)
bic1 = matrix(NA,8,8)
for(p in 0:7)
{
  for(q in 0:7)
  {
    a.p.q = Arima(data$log_BONDS,order=c(p,0,q),include.mean=TRUE)
    aic.p.q = a.p.q$aic
    bic.p.q = BIC(a.p.q)
    aic1[p+1,q+1] = aic.p.q
    bic1[p+1,q+1] = bic.p.q
  }
}
aic1 
bic1 # 1,0 has the lowest BIC

# 2.2) Using the results for the optimal ARIMA model
arima_model_BIC <- Arima(data$log_BONDS, order = c(1,0,0), include.mean=TRUE)
summary(arima_model_BIC)

########################################################################################################################

################################# 3.) Testing for ARCH effects #######################################
# 3.1) Using the LM test
LM=function(x,h)
{
  n=length(x)
  x2=x^2-mean(x^2)
  dat<-matrix(,n-h,h+1)
  for (i in 1:(h+1))
  {
    dat[,i]=x2[(h+2-i):(n-i+1)]
  }
  a=lm(dat[,1]~dat[,2:(h+1)])
  r2=summary(a)$r.squared
  print(r2 * n)
  print(1-pchisq(r2*n,h))
}

LM(data$log_BONDS, 20) # The results show that we have clearly ARCH / GARCH effects in our series.

# 3.2) AFC and PAFC of the residuals and the squared residuals of the ARIMA (1, 0) model
par(mfrow=c(2,2))
Acf(arima_model_BIC$residuals, type= "correlation", lag= 15, main= "ACF of residuals (Bonds)")
Pacf(arima_model_BIC$residuals, lag= 15, main= "PACF of residuals (Bonds)")

Acf(arima_model_BIC$residuals^2, type= "correlation", lag= 15, main= "ACF of squared residuals (Bonds)")
Pacf(arima_model_BIC$residuals^2, lag= 15, main= "PACF of squared residuals (Bonds)")

################################# 4.) ARMA-GARCH modeling ###########################################
# 4.1 ARMA - GARCH joint order selection
final.bic = Inf
final.order.arma = c(0,0)
final.order.garch = c(0,0)
for (p in 0:3) for (q in 0:3) for (d in 0:2) for (w in 0:2)
{
  spec = ugarchspec(variance.model=list(garchOrder=c(p,q)),
                    mean.model=list(armaOrder=c(d, w), include.mean=T),
                    distribution.model="std")    
  fit = ugarchfit(spec, data$log_BONDS, solver = 'hybrid')
  current.bic = infocriteria(fit)[2] 
  if (current.bic < final.bic) 
  {
    final.bic = current.bic
    final.order.arma = c(d, w)
    final.order.garch = c(p,q)
  }
}
final.order.arma
final.order.garch
# Select model with smallest BIC (if prediction is the objective). This would be ARMA (1, 0) and GARCH (1, 1)

# 4.2 Fit the GARCH model
m1_bonds=garchFit(data$log_BONDS~ arma(1,0) + garch(1,1),trace=F,data= data$log_BONDS, cond.dist = c("std"), include.mean = TRUE)
summary(m1_bonds)

# 4.3 AFC and PAFC on GARCH residuals and squared residuals
par(mfrow=c(2,2))
standardized_residuals <- residuals(m1_bonds, standardize = T) # standardize the residuals from the previous GARCH model
# AFC and PAFC on GARCH residuals
acf_residuals_BIC <- Acf(standardized_residuals, lag = 20, type = "correlation",main = "ACF ARMA (1,0) - GARCH (1,1) residuals")
pacf_residuals_BIC <- Pacf(standardized_residuals, lag = 20,main = "PACF ARMA (1,0) - GARCH (1,1) residuals") 
# However, our residuals reveal no boundary violations.

# AFC and PAFC on GARCH squared residuals
acf_squared_residuals_BIC <- Acf(standardized_residuals^2, lag = 20, type = "correlation",main = "ACF ARMA (1,0) - GARCH (1,1) squared residuals")
pacf_squared_residuals_BIC <- Pacf(standardized_residuals^2, lag = 20, main = "PACF ARMA (1,0) - GARCH (1,1) squared residuals")
# However, our squared residuals one several boundary violations.

# 4.4 Check residuals for normality
#fat tails
jarque.bera.test(standardized_residuals)
qqnorm(standardized_residuals) 
qqline(standardized_residuals)

# The Jarque Bera Test clearly rejects the fact that the standardized residuals of the GARCH model are normally distributed.
# This can be also seen in the QQ-Plot, concluding that we have fat tails.
```

## COMMODITIES
```{r}
################################# 1.) Testing stationarity ###########################################
# 1.1) Unit Root Test

# On raw series
augmented_df_test <- ur.df(data$`Last Price COMMODITIES`, selectlags = "BIC")
summary(augmented_df_test)

# On differenced series
augmented_df_test <- ur.df(data$log_Commodities, selectlags = "BIC")
summary(augmented_df_test)

# The test clearly shows that there is stationarity on the differenced series on stocks.
# However, it can be obtainted, that we also have stationarity on our raw series on the 95% CI.

# 1.2) Box-Ljung Test
Box.test(data$`Last Price COMMODITIES`, lag = 20, type = "Ljung")
Box.test(data$log_Commodities, lag = 20, type = "Ljung")

# 1.3) AFC and PAFC
par(mfrow=c(2,2))

#ACF and PACF on raw bond series.
Acf(data$`Last Price COMMODITIES`, type= "correlation", lag.max = 15,
    main= "ACF raw bond series")
Pacf(data$`Last Price COMMODITIES`, lag= 15, main= "PACF raw bond series")

#ACF and PACF differenced process
Acf(data$log_Commodities, type= "correlation", lag= 15, main= "ACF of differenced process")
Pacf(data$log_Commodities, lag= 15, main= "PACF of differenced process")

####################################### 2.) ARMA modeling ###########################################
# 2.1) Identify the ARIMA model
aic1 = matrix(NA,8,8)
bic1 = matrix(NA,8,8)
for(p in 0:7)
{
  for(q in 0:7)
  {
    a.p.q = Arima(data$log_Commodities,order=c(p,0,q),include.mean=TRUE)
    aic.p.q = a.p.q$aic
    bic.p.q = BIC(a.p.q)
    aic1[p+1,q+1] = aic.p.q
    bic1[p+1,q+1] = bic.p.q
  }
}
aic1 
bic1 # 0,0 has the lowest BIC

# 2.2) Using the results for the optimal ARIMA model
arima_model_BIC <- Arima(data$log_Commodities, order = c(0,0,0), include.mean=TRUE)
summary(arima_model_BIC)

################################ 3.) Testing for ARCH effects #######################################
# 3.1) Using the LM test
LM=function(x,h)
{
  n=length(x)
  x2=x^2-mean(x^2)
  dat<-matrix(,n-h,h+1)
  for (i in 1:(h+1))
  {
    dat[,i]=x2[(h+2-i):(n-i+1)]
  }
  a=lm(dat[,1]~dat[,2:(h+1)])
  r2=summary(a)$r.squared
  print(r2 * n)
  print(1-pchisq(r2*n,h))
}

LM(data$log_Commodities, 20) # The results show that we have clearly ARCH / GARCH effects in our series.

# 3.2) AFC and PAFC of the residuals and the squared residuals of the ARIMA (1, 0) model
par(mfrow=c(2,2))
Acf(arima_model_BIC$residuals, type= "correlation", lag= 15, main= "ACF of residuals (Commodities)")
Pacf(arima_model_BIC$residuals, lag= 15, main= "PACF of residuals (Commodities)")

Acf(arima_model_BIC$residuals^2, type= "correlation", lag= 15, main= "ACF of squared residuals (Commodities)")
Pacf(arima_model_BIC$residuals^2, lag= 15, main= "PACF of squared residuals (Commodities)")

##################################### 4.) ARMA-GARCH modeling ####################################
# 4.1 ARMA - GARCH joint order selection
final.bic = Inf
final.order.arma = c(0,0)
final.order.garch = c(0,0)
for (p in 0:3) for (q in 0:3) for (d in 0:2) for (w in 0:2)
{
  spec = ugarchspec(variance.model=list(garchOrder=c(p,q)),
                    mean.model=list(armaOrder=c(d, w), include.mean=T),
                    distribution.model="std")    
  fit = ugarchfit(spec, data$log_Commodities, solver = 'hybrid')
  current.bic = infocriteria(fit)[2] 
  if (current.bic < final.bic) 
  {
    final.bic = current.bic
    final.order.arma = c(d, w)
    final.order.garch = c(p,q)
  }
}
final.order.arma
final.order.garch
# Select model with smallest BIC (if prediction is the objective). This would be ARMA (1, 0) and GARCH (1, 1)

# 4.2 Fit the GARCH model
m1_commodities=garchFit(data$log_Commodities~ arma(0,0) + garch(1,1),trace=F,data= data$log_Commodities, cond.dist = c("std"), include.mean = TRUE)
summary(m1_commodities)

# 4.3 AFC and PAFC on GARCH residuals and squared residuals
par(mfrow=c(2,2))
standardized_residuals <- residuals(m1_commodities, standardize = T) # standardize the residuals from the previous GARCH model
# AFC and PAFC on GARCH residuals
acf_residuals_BIC <- Acf(standardized_residuals, lag = 20, type = "correlation",main = "ACF ARMA (0,0) - GARCH (1,1) residuals")
pacf_residuals_BIC <- Pacf(standardized_residuals, lag = 20,main = "PACF ARMA (0,0) - GARCH (1,1) residuals") 
# However, our residuals reveal one boundary violations.

# AFC and PAFC on GARCH squared residuals
acf_squared_residuals_BIC <- Acf(standardized_residuals^2, lag = 20, type = "correlation",main = "ACF ARMA (0,0) - GARCH (1,1) squared residuals")
pacf_squared_residuals_BIC <- Pacf(standardized_residuals^2, lag = 20, main = "PACF ARMA (0,0) - GARCH (1,1) squared residuals")
# However, our squared residuals no several boundary violations.

# 4.4 Check residuals for normality
#fat tails
jarque.bera.test(standardized_residuals)
qqnorm(standardized_residuals) 
qqline(standardized_residuals)

# The Jarque Bera Test clearly rejects the fact that the standardized residuals of the GARCH model are normally distributed.
# This can be also seen in the QQ-Plot, concluding that we have fat tails.
```

# DCC-GARCH
```{r pressure, fig.keep="all"}
rX <- data[c('Date', 'log_Crypto', 'log_STOXX', 'log_BONDS', 'log_Commodities')] # Create subset
rX <- xts(rX[, -1], order.by=as.Date(data$Date)); # Convert to xts object

spec_cry <- ugarchspec(variance.model = list(garchOrder = c(1,1)), mean.model = list(armaOrder = c(1,1)), distribution.model = "std")
spec_stoxx <- ugarchspec(variance.model = list(garchOrder = c(1,1)), mean.model = list(armaOrder = c(0,0)), distribution.model = "std")
spec_bonds <- ugarchspec(variance.model = list(garchOrder = c(1,1)), mean.model = list(armaOrder = c(1,0)), distribution.model = "std")
spec_commodities <- ugarchspec(variance.model = list(garchOrder = c(1,1)), mean.model = list(armaOrder = c(1,0)), distribution.model = "std")

mspec = multispec( c(spec_cry, spec_stoxx, spec_bonds, spec_commodities))

multf = multifit(mspec, rX)

# spec1 = dccspec(uspec = mspec, dccOrder = c(1, 1), distribution = 'mvnorm') # multivariate normal distribution
spec1 = dccspec(uspec = mspec, dccOrder = c(1, 1), distribution = 'mvt') # multivariate student t distribution
fit1 = dccfit(spec1, data = rX, fit.control = list(eval.se = TRUE), fit = multf)

print(fit1)

corr_mat <-rcor(fit1)

corr_cry_stoxx <-corr_mat[1,2,]
corr_cry_stoxx <-as.xts(corr_cry_stoxx)
mean(corr_cry_stoxx)

corr_cry_bonds <-corr_mat[1,3,]
corr_cry_bonds <- as.xts(corr_cry_bonds)
mean(corr_cry_bonds)

corr_cry_commo <- corr_mat[1,4,]
corr_cry_commo <- as.xts(corr_cry_commo)
mean(corr_cry_commo)

corr_bonds_stocks <- corr_mat[3,2,]
corr_bonds_stocks <- as.xts(corr_bonds_stocks)

corrxx <- merge(corr_cry_stoxx, corr_cry_bonds, corr_cry_commo)

plot(corr_cry_bonds)
plot(corr_cry_commo)
plot(corr_bonds_stocks)
```

# DCC Plots
```{r}
par(mfrow=c(1,1))
plot.xts(corrxx, screens = factor(1, 1), ylim=range(c(-0.3,0.4)), main='Conditional Correlation: Cryptos/Stocks, Cryptos/Bonds, Cryptos/Commodities')
addLegend("bottomleft",         
       legend.names = c("Cryptos/Stocks", "Cryptos/Bonds", "Cryptos/Commodities"),  
       col = c("black", "red", "green"),  
       lty=c(1,1,1),
       lwd = c(2,2,2))
addEventLines(events_covid, srt=90, pos=2, col = "red")


plot(corr_cry_stoxx, ylim=range(c(-0.5,0.5)), main='Conditional Correlation: Stocks/Cryptos')

plot(corr_cry_bonds, main='Conditional Correlation: Cryptos/Bonds') 
#abline(h = 0.033, col = "red")
legend(1591550270, -0.02532262,          # Position
       legend = c("DCC", "mean"),  # Legend texts
       col = c("black", "red"),           # Line colors
       lwd = 2) 

plot(corr_cry_stoxx, main='Conditional Correlation: Cryptos/Stocks') 
#abline(h = 0.145, col = "red")
legend(1591550270, 0.03,          # Position
       legend = c("DCC", "mean"),  # Legend texts
       col = c("black", "red"),           # Line colors
       lwd = 2) 

plot(corr_cry_commo, main='Conditional Correlation: Cryptos/Commodities') 
#abline(h = 0.08, col = "red")
legend(1591550270, -0.02532262,          # Position
       legend = c("DCC", "mean"),  # Legend texts
       col = c("black", "red"),           # Line colors
       lwd = 2) 
```



